The Rapid Cycleway Prioritisation Tool

### 2020-06-18 rapid-slides.Rmd
Tweaks

```{r, engine='bash', eval=FALSE, echo=FALSE}
# 🛣🚲🚀
cp rapid-slides.html popupCycleways/v1/slides/index.html
cp -Rv libs popupCycleways/v1/slides/
cd popupCycleways
git status
git add -A
git commit -am 'Add slides'
git push
cd -
```

>>>>

```{r, engine='bash', eval=FALSE, echo=FALSE}
# 🛣🚲🚀
cp rapid-slides.html popupCycleways/v1/slides/index.html
cp -Rv libs popupCycleways/v1/slides/
cd popupCycleways
git status
git diff
git add -A
git commit -am 'Add slides'
git push
cd -
```
